From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/ufin.tex
Even more fixes

Using categorical language, the setting for the semantics in the previous section is the category of finite sets and
functions $\SetFin$. However, as $\PiLang$ only refers to bijective functions, a more precise setting is the groupoid
$\BFin = \term{core}(\SetFin)$ of finite sets and bijections. $\SetFin$ has finite coproducts $(\emptyt, \sqcup)$ and
finite products $(\unit, \times)$ and in $\BFin$ these restrict to additive and multiplicative symmetric monoidal
structures, respectively, making $\BFin$ a symmetric rig groupoid -- the \emph{vertical categorification} of the
commutative rig of natural numbers $\Nat$.

@@

  Another HIT that we use is the set-quotient $\quot{A}{R}$ which takes an $\hSet$ $A$ and a relation $R : A \to A \to
    \UU$. It has an inclusion of points $q : A \to \quot{A}{R}$, and adds paths between related pairs of elements
  $\quotrel : R(x,y) \to q(x) \id_{\quot{A}{R}} q(y)$ (see~\cref{def:set-quot}).  We recall that the quotient is
  \emph{effective} if $R$ is a prop-valued equivalence relation, that is, $R(x,y)$ holds iff $(q(x) \id_{\quot{A}{R}}
    q(y))$.

  \begin{definition}[Set Quotient]
    \label{def:set-quot}
    Given a type $A$ which is an $\hSet$, and a relation $R : A \to A \to \hProp$, the set-quotient $\quot{A}{R}$ is the
    higher inductive type generated by
    \begin{itemize}
      \item an inclusion function $q : A \to \quot{A}{R}$,
      \item for each $x, y : A$ such that $R(x,y)$, a path $q(x) \id_{\quot{A}{R}} q(y)$,
      \item a set truncation, for each $x, y : \quot{A}{R}$ and $r, s : x \id_{\quot{A}{R}} y$, we have $r \id s$,
    \end{itemize}
    with an appropriate induction principle.
  \end{definition}

>>>>

Using categorical language, the setting for the semantics in the previous section is the category of finite sets and
functions $\SetFin$. However, as $\PiLang$ only refers to bijective functions, a more precise setting is the groupoid
$\BFin = \term{core}(\SetFin)$ of finite sets and bijections. $\SetFin$ has finite coproducts $(\emptyt, \sqcup)$ and
finite products $(\unit, \times)$ and in $\BFin$ these restrict to additive and multiplicative symmetric monoidal
structures, respectively, making $\BFin$ a symmetric rig groupoid -- the \emph{vertical categorification} of the
commutative rig of natural numbers $\Nat$~\cite{baezHIGHERDIMENSIONALALGEBRA}.

@@

  Another HIT that we use is the set-quotient $\quot{A}{R}$ which takes an set $A$ and a relation $R : A \to A \to \UU$.
  It has an inclusion of points $\quotinc : A \to \quot{A}{R}$, and adds paths between related pairs of elements
  $\quotrel : R(x,y) \to \quotinc(x) \id_{\quot{A}{R}} \quotinc(y)$ (see~\cref{def:set-quot}).  We recall that the
  quotient is \emph{effective} if $R$ is a prop-valued equivalence relation, that is, $R(x,y)$ holds iff $(q(x)
  \id_{\quot{A}{R}} q(y))$.

  \begin{definition}[Set Quotient]
    \label{def:set-quot}
    Given a type $A$ which is a set, and a relation $R : A \to A \to \UU$, the set-quotient $\quot{A}{R}$ is the higher
    inductive type generated by
    \begin{itemize}
      \item an inclusion function $\quotinc : A \to \quot{A}{R}$,
      \item for each $x, y : A$ such that $R(x,y)$, a path $\quotinc(x) \id_{\quot{A}{R}} \quotinc(y)$,
      \item a set truncation, for each $x, y : \quot{A}{R}$ and $r, s : x \id_{\quot{A}{R}} y$, we have $r \id s$,
    \end{itemize}
    with an appropriate induction principle.
  \end{definition}
